Stack Safety as a Security Property

### 2020-07-08 main.tex
call map -> function map

\definition{Transition} Given a trace $\MPT$, a call map $\callmap$ and
a code map $\codemap$, an $n$-{\em transition} is a pair of
machine-policy state pairs $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$
in the trace such that:
\begin{itemize}
\item one state pair steps to the other:
  $$\exists \obs. ~ (\mach_c, \pol_c) \stepstopol{\obs} (\mach_e, \pol_e),$$
\item $\mach_c$ is a valid call with $n$ arguments:
  $$\callmap(\mach_c(\PCname)) = n,$$
\item and $\mach_e$ is an entry point for $f$:
  $$\codemap(\mach_e(\PCname)) = f.$$
\end{itemize}

\definition{Stack Integrity} Let $\callmap$ be a call map and
$\codemap$ a code map. We say that a system satisfies {\em stack
  integrity} with respect to $\callmap$ and $\codemap$ if, for every
initial machine-policy state pair $(\mach_0, \pol_0)$ and its induced
trace $\MPT$, and every $n$-transition $(\mach_c, \pol_c)$ and
$(\mach_e, \pol_e)$ in $\MPT$, the prefix $\MPT_{pre}$ of $\MPT$ from
$(\mach_e, \pol_e)$ until the first return corresponding to $\mach_c$
(if any) satisfies trace integrity with respect to the contour at the
call:
%
$$\forall \MPT_{pre}. ~ \mpstate{\mach_e}{\pol_e} \hookrightarrow_P
\MPT_{pre} ~ | ~ \ret{\mach_c} \Rightarrow
\mathit{int}~\mathit{Cof}(\mach_c, n)~\MPT_{pre}$$

@@

\definition{Stack Confidentiality}
Let $\callmap$ be a call map and $\codemap$ a code map. We say that a
system satisfies {\em stack confidentiality} with respect to
$\callmap$ and $\codemap$ if, for every initial machine-policy state
pair $(\mach_0, \pol_0)$ and its induced trace $\MPT$, and every
$n$-transition $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$ to a callee
$f$ in $\MPT$, the following holds. Let $\MPT_{\mathit{call}}$ be the prefix where
\(\mpstate{\mach_e}{\pol_e} \hookrightarrow_P \MPT_{\mathit{call}} | \ret{\mach_c}\).
For each variant state \(\mach_e' \approx_{\mathit{Cof}(\mach_c, f, n)}
\mach_e\), let \(\machT\) be the similarly prefixed trace such that
\(\mach_e' \hookrightarrow \machT\). Then trace confidentiality holds on
\(\MPT_{\mathit{call}}\) and \(\machT\) with regard to \(\mathit{Cof}(\mach_c, f, n)\)
and \(R = \ret{\mach_c}\):

@@

To formally capture this aspect of stack safety, we introduce three
security properties that rely on the underlying knowledge of the
program structure (code maps, function maps, return maps, and entry
maps): {\em control separation} ensures the validity of transition
sources between functions, {\em entry integrity} ensures the validity
of call targets, and {\em return integrity} ensures the validity of
return targets.

@@

\definition{Eager testing property}
  Let $\callmap$ a call map and $\codemap$ a code map. Given a state
  $(\mach, \pol) \in \MPS$ that is well-formed w.r.t. a variant stack $\vs$, we
  say that an MP-trace induced from $(\mach, \pol)$ satisfies the \emph{eager
  testing property} at a given call depth if:

@@

    \definition{Observable Stack Safety}
      A system enjoys {\em observable stack safety} with regard to a call map
      and a code map if it enjoys both observable stack integrity and
      observable stack confidentiality with regard to them.

>>>>

\definition{Transition} Given a trace $\MPT$, a call map $\callmap$ and
a function map $\codemap$, an $n$-{\em transition} is a pair of
machine-policy state pairs $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$
in the trace such that:
\begin{itemize}
\item one state pair steps to the other:
  $$\exists \obs. ~ (\mach_c, \pol_c) \stepstopol{\obs} (\mach_e, \pol_e),$$
\item $\mach_c$ is a valid call with $n$ arguments:
  $$\callmap(\mach_c(\PCname)) = n,$$
\item and $\mach_e$ is an entry point for $f$:
  $$\codemap(\mach_e(\PCname)) = f.$$
\end{itemize}

\definition{Stack Integrity} Let $\callmap$ be a call map and
$\codemap$ a function map. We say that a system satisfies {\em stack
  integrity} with respect to $\callmap$ and $\codemap$ if, for every
initial machine-policy state pair $(\mach_0, \pol_0)$ and its induced
trace $\MPT$, and every $n$-transition $(\mach_c, \pol_c)$ and
$(\mach_e, \pol_e)$ in $\MPT$, the prefix $\MPT_{pre}$ of $\MPT$ from
$(\mach_e, \pol_e)$ until the first return corresponding to $\mach_c$
(if any) satisfies trace integrity with respect to the contour at the
call:
%
$$\forall \MPT_{pre}. ~ \mpstate{\mach_e}{\pol_e} \hookrightarrow_P
\MPT_{pre} ~ | ~ \ret{\mach_c} \Rightarrow
\mathit{int}~\mathit{Cof}(\mach_c, n)~\MPT_{pre}$$

@@

\definition{Stack Confidentiality}
Let $\callmap$ be a call map and $\codemap$ a function map. We say that a
system satisfies {\em stack confidentiality} with respect to
$\callmap$ and $\codemap$ if, for every initial machine-policy state
pair $(\mach_0, \pol_0)$ and its induced trace $\MPT$, and every
$n$-transition $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$ to a callee
$f$ in $\MPT$, the following holds. Let $\MPT_{\mathit{call}}$ be the prefix where
\(\mpstate{\mach_e}{\pol_e} \hookrightarrow_P \MPT_{\mathit{call}} | \ret{\mach_c}\).
For each variant state \(\mach_e' \approx_{\mathit{Cof}(\mach_c, f, n)}
\mach_e\), let \(\machT\) be the similarly prefixed trace such that
\(\mach_e' \hookrightarrow \machT\). Then trace confidentiality holds on
\(\MPT_{\mathit{call}}\) and \(\machT\) with regard to \(\mathit{Cof}(\mach_c, f, n)\)
and \(R = \ret{\mach_c}\):

@@

To formally capture this aspect of stack safety, we introduce three
security properties that rely on the underlying knowledge of the
program structure (call maps, function maps, return maps, and entry
maps): {\em control separation} ensures the validity of transition
sources between functions, {\em entry integrity} ensures the validity
of call targets, and {\em return integrity} ensures the validity of
return targets.

@@

\definition{Eager testing property}
  Let $\callmap$ a call map and $\codemap$ a function map. Given a state
  $(\mach, \pol) \in \MPS$ that is well-formed w.r.t. a variant stack $\vs$, we
  say that an MP-trace induced from $(\mach, \pol)$ satisfies the \emph{eager
  testing property} at a given call depth if:

@@

    \definition{Observable Stack Safety}
      A system enjoys {\em observable stack safety} with regard to a call map
      and a function map if it enjoys both observable stack integrity and
      observable stack confidentiality with regard to them.
